Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance

### 2019-06-05 Manuscript/manuscript.Rmd
editted table 1

**Table 1. TAD boundaries are the minority of the genome, creating high class imbalance ratio irrespectively of resolution.**

| Resolution (Bin Width) | Median Number of Genomic Bins (IQR) | Median Number of TADs (IQR) | Median Number of TAD Boundaries (IQR) | Median Imbalance Ratio (IQR) |
|------------------------|-------------------------------------|-----------------------------|---------------------------------------|------------------------------|
| 10 kb                  | 13055 (8961)                        | 380 (203)                   | 1338 (832)                            | 0.11 (0.02)                  |
| 25 kb                  | 5226 (3586)                         | 220 (155)                   | 737 (521)                             | 0.17 (0.02)                  |
| 50 kb                  | 2616 (1794)                         | 110 (86)                    | 367 (294)                             | 0.17 (0.02)                  |
| 100 kb                 | 1310 (897)                          | 53 (37)                     | 169 (136)                             | 0.15 (0.02)                  |

>>>>

**Table 1. Sparce TAD boundaries throughout the linear genome create high imbalance ratios irrespective of resolution.**

| Resolution (Bin Width) | Average Number of Genomic Bins (SD) | Average Number of TAD Boundaries (SD) | Average Imbalance Ratio (SD) |
|------------------------|-------------------------------------|---------------------------------------|------------------------------|
| 10 kb                  | 12214.1 (6068.5)                    | 1254.6 (598.8)                        | 0.12 (0.02)                  |  
| 25 kb                  | 4892.7 (2431.2)                     | 714.0 (358.4)                         | 0.17 (0.01)                  |
| 50 kb	                 | 2450.9 (1217.6)                     | 364.4 (184.5)                         | 0.17 (0.01)                  |
| 100 kb                 | 1227.5 (609.8)                      | 165.3 (90.9)                          | 0.15 (0.02)                  |
